### 2018-04-13 reports/thesis/chapters/5_inference.tex
Adjusted a few bib entries.

The resulting $z$ statistics and $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Significant pixels were chosen for $\|z\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} algorithm at the $z_\alpha = 2$ significance level. The significant pixels are shown in Figure \ref{fig:inference_initial_artist_sig_pixels}.

@@

\cite{efron2004large} was motivated to tackle problems observed in large scale multiple hypothesis testing, for example in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}. These problems are similar to the one observed at the start of this chapter. The empirical null is now used widely, including in neuroimaging \citep{schwartzman2008false,schwartzman2009empirical}.

@@

The BH procedure can be conducted, corrected for the empirical null. The $p$-values are shown in \ref{fig:inference_alt_empirical_z_p_values}, a number of them are significant. The significant pixels are shown in red in Figure \ref{fig:inference_alt_empirical_z_image}. The majority of the significant pixels are cluster together and highlighting the defect. Not all of the defect was tested positive, but a good number of them are. This should be enough to raise suspicion in that particular area.

@@

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_z_image.eps}
        \caption{$z$ image}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_p_image.eps}
        \caption{$\log p$-value image}
    \end{subfigure}
    }
    \caption{The $z$ image and $p$-value image after using the empirical null filter.}
    \label{fig:inference_filter_z_p_image}
\end{figure}

@@

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_pvalues.eps}
        \caption{$\log p$-values}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_sig.eps}
        \caption{$z$ image with red significant pixels}
    \end{subfigure}
    }
    \caption{The $p$-values and significant pixels when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane with gradient 7.0.}
    \label{fig:inference_NoDefect_Plane_p_sig}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_pvalues.eps}
        \caption{$\log p$-values}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_sig.eps}
        \caption{$z$ image with red significant pixels}
    \end{subfigure}
    }
    \caption{The $p$-values and significant pixels when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid with amplitude $10^4$.}
    \label{fig:inference_NoDefect_Sinusoid_p_sig}
\end{figure}

@@

These examples showed that the empirical null filter corrected the test statistics accordingly. However in extreme cases, the empirical null filter can fail producing clusters of low $p$-values giving an illusion of a defect. In practice, extreme cases should not happen. Referring back to the real life example in Figure \ref{fig:inference_filter_mean_null}, the empirical null mean only varied around $0\pm3$ which is a small variation compared to Figure \ref{fig:inference_NoDefect_nullmean}.

@@

>>>>

The resulting $z$ statistics and $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Significant pixels were chosen for $\|z\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} (BH) procedure at the $z_\alpha = 2$ significance level. The significant pixels are shown in Figure \ref{fig:inference_initial_artist_sig_pixels}.

@@

\cite{efron2004large} was motivated to tackle problems observed in large scale multiple hypothesis testing, for example in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}. These problems are similar to the one observed at the start of this chapter. The empirical null is now used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}.

@@

The BH procedure can be conducted, corrected for the empirical null. The $p$-values are shown in \ref{fig:inference_alt_empirical_z_p_values}, a number of them are significant. The significant pixels are shown in red in Figure \ref{fig:inference_alt_empirical_z_image}. The majority of the significant pixels are cluster together and highlighting the defect. Not all of the defects were tested positive, but a good number of them are. This should be enough to raise suspicion in that particular area.

@@

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_z_image.eps}
        \caption{$z$ image}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_p_image.eps}
        \caption{$-\log p$-values}
    \end{subfigure}
    }
    \caption{The $z$ image and $p$-value image after using the empirical null filter.}
    \label{fig:inference_filter_z_p_image}
\end{figure}

@@

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_pvalues.eps}
        \caption{$\log p$-values}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_sig.eps}
        \caption{$z$ image with red significant pixels}
    \end{subfigure}
    }
    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane with gradient 7.0.}
    \label{fig:inference_NoDefect_Plane_p_sig}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_pvalues.eps}
        \caption{$\log p$-values}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_sig.eps}
        \caption{$z$ image with red significant pixels}
    \end{subfigure}
    }
    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid with amplitude $10^4$.}
    \label{fig:inference_NoDefect_Sinusoid_p_sig}
\end{figure}

@@

These examples showed that the empirical null filter corrected the test statistics accordingly. However in extreme cases, the empirical null filter can fail and producing clusters of low $p$-values giving an illusion of a defect. In practice, extreme cases should not happen. Referring back to the real life example in Figure \ref{fig:inference_filter_mean_null}, the empirical null mean only varied around $0\pm3$ which is a small variation compared to Figure \ref{fig:inference_NoDefect_nullmean}.

@@

receiver operating characteristic \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use}
